\cvsection{Projects}
\cvproject{Geometric deep learning for subcortical brain shape analysis - Master thesis project}
\begin{itemize}
\item Implementing and evaluating geometric deep learning models for classification and regression tasks
\item Investigating the correlation between the brain geometry and subject features (e.g hypertension, smoking status) 
\end{itemize}
\smallskip
\cvproject{Grid-world reinforcement learning agent}
\begin{itemize}
    \item Applied Deep Q-Learning techniques to develop an agent which learns to find a path to the target in a grid world maze. My submission was selected as one of the best in the Reinforcement Learning course.
\end{itemize}
\smallskip
\cvproject{Tweets generator - LSTM based model}
\begin{itemize}
\item Scrapes all tweets from a given account, trains a LSTM model to generate tweets.
\item React app with interface decide which tweets to publish from the generated suggestions.
\item Result: generated tweets are funny and engaging, I had few accounts running in the past.
\item \href{https://github.com/jedrazb/twitter-bot-controller}{https://github.com/jedrazb/twitter-bot-controller}
\end{itemize}
\smallskip
\cvproject{Neural Network Library (for multi-layer perceptron)}
\begin{itemize}
\item Developed library with keras-like structure from scratch using numpy, for now it supports Dense Layers and various loss functions .
\item Used my library to develop models to classify:
\smallskip
\begin{itemize}
    \item iris dataset (98.7\% accuracy)
    \item MINST handwritten digits (97.8\% accuracy)
\end{itemize}
\item \href{https://github.com/jedrazb/python-neural-network}{https://github.com/jedrazb/python-neural-network}
\end{itemize}
\cvproject{Visualiser for simulated annealing applied to the TSP}
\begin{itemize}
\item Applied simulated annealing heuristic to the Traveling Salesman Problem.
\item Implemented visualisation interface to observe the process of learning.
\item 17 stars on Github and counting.
\item \href{https://github.com/jedrazb/python-tsp-simulated-annealing}{https://github.com/jedrazb/python-tsp-simulated-annealing}
\end{itemize}
\cvproject{HealthClaim - decentralized storage of medical records (3rd year group project)}
\begin{itemize}
\item Used Hyperledger Indy to design a transparent and secure system for decentralized medical record storage.
\item Main features: users can decide where their medical records are stored, users give explicit permission for access, users can generate Zero-knowledge proofs without disclosure of medical records.
\item Project was carried out with cooperation with Sovrin Foundation.
\end{itemize}
\smallskip

